%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{}
% {Mrs. Jane Smith \\
% Recruitment Officer \\
% The Corporation \\
% 123 Pleasant Lane \\
% City, State 12345} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Qing Wang \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
1648 80th St. APT 2R \\ Brooklyn, New York 11214 \\ (929) 888-3746 % Your address and phone number
\end{center} 
\vfill

\signature{Qing Wang} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Recruiting Manager,} 
 
I am writing to apply for the position Software Engineer University of EMC. I know this position from the Indeed. As I have checked the information for this job. I believe that my education and experiences make me a qualified candidate for this position.

Due to the hard work on course study of the past years, I gain solid knowledge in the area of Computer Science and Engineering, like Operating Systems, Databases, Networking and Object-Oriented Programming. The project for the course Principle Database Systems let me started with Web Design, from the back-end to the front-end. I gained basic the skill of web development with LAMP after finishing this project.

I used to serve a Software Engineer Intern at AdminSys Inc, a startup that just established at earlier time this year. The past two months’ professional experience helps me understand to some degree the whole process of developing products, from requirements to design, coding, testing, deployment and Maintenance.

As a quick learner and self-starter, I can quickly get adapted to new Environments and learn new knowledge and skills. All the experiences and properties that I have will help me to be an outstanding software engineer. 

I would greatly appreciate the chance to work for EMC and make my contribution with the related Experience and also develop myself through working with outstanding Software Engineers. I am looking forward to meet with you to discuss this position in further detail. Please feel free to contact me at your convenience by phone (929-888-3746) or email (qw422@nyu.edu).

Thanks for your time and consideration.

\closing{Sincerely yours,}


% \encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}