% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
 
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Kai Wang}

% {E-mail}{mobilephone}{homepage}
\contactInfo{kw1701@nyu.edu}{(+1) 347-698-8475}{https://goo.gl/55BczI}
% {E-mail}{mobilephone}
%\basicContactInfo{xxx@kingwang.me}{(+1) 929-888-3746}

\section{\faUser\ Objective}
To obtain a Financial analysis / Data analysis position from an organization where I can bring my dedication, responsibility and passion and utilize my educational qualifications.
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{New York University (NYU)}, New York}{Sept 2014 -- May 2016}
\textit{Master of Science} in Financial and Risk Engineering (3.78/4.0) \\
\textit{Courses} : Big Data in Finance, Financial Computing(C++), Quantitative Methods in Fin
\datedsubsection{\textbf{Central University of Finance and Economics}, Beijing, China}{Sept 2010 -- July 2014}
\textit{Bachelor of Science} in Mathematics and Financial Mathematics (83/100) \\
\textit{Courses} : Advanced Programming Language(C), Computation to Financial Engineering(Matlab)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Industrial and Commercial Bank of China Ltd.} Beijing, China}{Sept 2012 -- Jan 2013}
\textbf{Analyst Assistant Intern}
\begin{itemize}
  \item Assisted with pension fund processing, provied clients with personal financial planning
  \item Assisted with issuing of credit and examining letter of credit
\end{itemize}

\section{\faCogs\ Projects}
\datedsubsection{\textbf{Financial Computing (C++, libcurl)}}{July 2015}
Evaluate the impact of earning report on stock price
\begin{itemize}
  \item Retrieved historical price data from Yahoo Finance with libcurl
  \item Created STL containers to manage the stock prices and earning information
  \item Operated stock data with classes and arithmetic operators overloading and generated Excel graphs with Excel driver
\end{itemize}

\datedsubsection{\textbf{R Packages Application (R)}}{Mar 2015}
Used R and Related Packages to do Financial data Analysis.
\begin{itemize}
  \item Estimated the copula parameters with copula packages.
  \item Tested multi-regression in factor model, GDP growth prediction with AR model.
\end{itemize}

\datedsubsection{\textbf{Financial Data Processing (Hadoop + R)}}{Mar 2015}
% \role{Hadoop, R}{Course Project for Financial Big Data}
Used Hadoop and R to compute the Relationships of different stock prices.
\begin{itemize}
  \item Written the Mapper and Reducer function to implement the linear regression Algorithm.
  \item Processed the 10 years of prices of set of stocks with MapReduce to get returns.
\end{itemize}

\datedsubsection{\textbf{Portfolio Risk Management Analysis}}{Nov 2014}
Developed macroeconomics factor models, fundamental factor models and statistical models to forecasting risks and potential returns.
\begin{itemize}
  \item Integrated data with lookup and reference functions.
  \item Tested multi-regression and principle component analysis model with some out-of-sample
\end{itemize}

\section{\faCog\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C++, Java, R, Matlab, SQL 
  \item Platform/Software: Excel, SPSS, MySQL, Hadoop
\end{itemize}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

\end{document}
