% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
 
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Qing Wang}

% {E-mail}{mobilephone}{homepage}
\contactInfo{qw422@nyu.edu}{(+1) 929-888-3746}{https://goo.gl/tBMWFF}
% {E-mail}{mobilephone}
%\basicContactInfo{xxx@kingwang.me}{(+1) 929-888-3746}

\section{\faUser\ Objective}
To obtain an SDE/SDET position from an organization where I can bring my dedication, responsibility and
passion and utilize my educational qualifications from NYU.
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{New York University (NYU)}, New York}{Sept 2013 -- May 2015}
\textit{Master of Science} in Electrical and Computer Engineering (ECE)
\datedsubsection{\textbf{BeijingJiaotong University}, Beijing, China}{Sept 2009 -- July 2013}
\textit{Bachelor of Science} in Biomedical Engineering (BME)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{AdminSys Inc.} New York}{June 2015 -- Aug 2015}
\textbf{Backend Development Intern}
\role{Node.js/Express, MongoDB/Monk}{PunchSystem Deveopment}
Development of Web App used for employee attendance records tracking
\begin{itemize}
  \item Designed the Modules to implement the CRUD of punch records and autority delegation.
  \item Optimized the performance of wage calculation by 70\% by applying aggregation.
  \item Built the basic UI with Jade and Test the APIs with Mocha.js and Mock-Express.
\end{itemize}

\section{\faCogs\ Projects}
\datedsubsection{\textbf{MyPinterest Web Application Design (PHP/MySQL)}}{May 2015}
% \role{PHP/MySQL, JavaScript, HTML/CSS}{Course Project for Principle of Database Systems}
Development of a social network application mostly used for photos shareing
\begin{itemize}
  \item Designed the ER model and transfered it to relational model
  \item Created the backend by using MySQL as database and PHP as the Sever side scripting language. 
  \item Build the UI with HTML/CSS and JavaScript to implement User Interactive.
\end{itemize}

% \datedsubsection{\textbf{Financial Data Processing (Hadoop + R)}}{Mar 2015}
% % \role{Hadoop, R}{Course Project for Financial Big Data}
% Us Hadoop and R to compute the Relationships of different stack prices.
% \begin{itemize}
%   \item Written the Mapper and Reducer function to implement the linear regression Algorithm.
%   \item Processed the 10 years of prices of set of stocks with MapReduce to get returns.
% \end{itemize}

\datedsubsection{\textbf{Lind-Fuse File System (Python, Ubuntu)}}{Nov 2014}
% \role{Python, Ubuntu}{Course Project for Operating Systems}
Implemented a basic block file system by modifying a given file system model without blocks.
\begin{itemize}
  \item Adjust/Add functions of System Calls for this new file system.
  \item Write a checker to check if the new file system works properly.
\end{itemize}

\datedsubsection{\textbf{Chatter Implementation(Java)}}{Nov 2014}
% \role{Python, Ubuntu}{Course Project for Operating Systems}
Implemented a Java command line chatter program that enabled users to chat instantly.
\begin{itemize}
  \item Wrote chatter client and chatter server programs in blocking and non-blocking versions.
  \item Used selector and channel from Java NIO package to solve concurrency issues.
\end{itemize}

\datedsubsection{\textbf{TIFF Format Image Processing (Java)}}{July 2014}
% \role{Java}{Side project}
Implemented Blurring, Edge Detection, and Run-length Encoding on TIFF format Images.
\begin{itemize}
  \item Blurring the image by applying the 3×3 window average algorithm to each pixel.
  \item Using Sobel edge detection algorithm to compute the approximate gradient of the color intensities.
  \item Image compressed by converting a Run-length Encoding to the image.
\end{itemize}

\section{\faCog\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming/Scripting Languages: Java > JavaScript == Python > PHP
  \item Development: MySQL, MongoDB, jQuery/Ajax, MVC, REST, JSON
  \item Platform/Software: Linux, Eclipse, Git
\end{itemize}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

\end{document}
