% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
 
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Zheng Wei}

% {E-mail}{mobilephone}{homepage}
\contactInfo{zw874@nyu.edu}{(+1) 347-935-6025}{https://goo.gl/GjQTz5}
% {E-mail}{mobilephone}
%\basicContactInfo{xxx@kingwang.me}{(+1) 929-888-3746}

\section{\faUser\ Objective}
To obtain a Financial analysis / Data analysis position from an organization where I can bring my dedication, responsibility and passion and utilize my educational qualifications.
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{New York University (NYU)}, New York}{Sept 2014 -- May 2016}
\textit{Master of Science} in Financial and Risk Engineering (3.9/4.0)
\datedsubsection{\textbf{Utah State University}, Beijing, China}{Aug 2011 -- Dec 2011}
Exchange Program (4.0/4.0) 
\datedsubsection{\textbf{BeijingJiaotong University}, Beijing, China}{Sept 2009 -- July 2013}
\textit{Bachelor of Science} in Accounting (3.8/4.0)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{New Times Trust Co., Ltd.} New York}{July 2013 -- Mar 2014}
\textbf{Analyst Assistant Intern}
\begin{itemize}
  \item Analyzed and calculated yield ratios and close positions etc. of Pledge of Stock Rights projects
  \item Executed analysis reports and due diligence reports
\end{itemize}

\datedsubsection{\textbf{PricewaterhouseCoopers} New York}{Jan 2013 -- Feb 2013}
\textbf{Associate Intern}
\begin{itemize}
  \item Assisted the Audit and Assurance Practice in annual audit of Kerry EAS headquarters 
  \item Managed balance sheet items, processed bank confirmations (about 500 files)
\end{itemize}

\section{\faCogs\ Projects}
\datedsubsection{\textbf{Financial Computing (C++, libcurl)}}{July 2015}
Evaluate the impact of earning report on stock price
\begin{itemize}
  \item Retrieved historical price data from Yahoo Finance with libcurl
  \item Created STL containers to manage the stock prices and earning information
  \item Operated stock data with classes and arithmetic operators overloading and generated Excel graphs with Excel driver
\end{itemize}

\datedsubsection{\textbf{Financial Data Processing (Hadoop + R)}}{Mar 2015}
% \role{Hadoop, R}{Course Project for Financial Big Data}
Used Hadoop and R to compute the Relationships of different stock prices.
\begin{itemize}
  \item Written the Mapper and Reducer function to implement the linear regression Algorithm.
  \item Processed the 10 years of prices of set of stocks with MapReduce to get returns.
\end{itemize}

\datedsubsection{\textbf{Portfolio Risk Management Analysis (Matlab, STATA, Excel)}}{Nov 2014}
Developed macroeconomics factor models, fundamental factor models and statistical models to forecasting risks and potential returns.
\begin{itemize}
  \item Integrated data with lookup and reference functions.
  \item Tested multi-regression and principle component analysis model with some out-of-sample.
\end{itemize}

\section{\faCog\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C++, R, Matlab, SQL
  \item Platform/Software: Excel, SPSS, MySQL, Hadoop
\end{itemize}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

\end{document}
